---
title: "p8105_hw2_zw2977"
author: "Ziqi Wang"
date: "2023-09-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Problem 2

```{r}

library(readxl)

library(dplyr)

library(tidyverse)



Trash_Wheel_Collection_Data <- read_excel("202309 Trash Wheel Collection Data.xlsx", 
               sheet = "Mr. Trash Wheel",
               range = "A3:N588", 
               col_names = c("Dumpster", "Month", "Year", "Date",                                    "Weight.tons",                 "Volume.cubic_yards",
                             "Plastic.Bottles", 
                             "Polystyrene", "Cigarette.Butts", 
                             "Glass.Bottles", 
                             "Plastic.Bags", "Wrappers",                                          "Sports.Balls", 
                             "Homes.Powered"))

names(Trash_Wheel_Collection_Data)


Trash_Wheel_Collection_Data.x <- Trash_Wheel_Collection_Data %>%                                    drop_na(Dumpster) %>% 
                 mutate(homes_powered = Weight.tons * 500/30,
                         origin = "Trash_Wheel")



```



```{r}
Professor_Trash_Wheel_Collection_Data <- read_excel("202309 Trash Wheel Collection Data.xlsx",                        
               sheet = "Professor Trash Wheel",
               range = "A3:M110", 
               col_names = c("Dumpster", "Month", "Year", "Date",                                    "Weight.tons", "Volume.cubic_yards",
                             "Plastic.Bottles", 
                             "Polystyrene", "Cigarette.Butts", 
                             "Glass.Bottles", 
                             "Plastic.Bags", "Wrappers",                                           "Homes.Powered"))



Professor_Trash_Wheel_Collection_Data.x <- Professor_Trash_Wheel_Collection_Data %>% 
                        drop_na(Dumpster)%>% 
               mutate(homes_powered = Weight.tons * 500/30, 
               origin = "Professor_Trash_Wheel")                        




```

```{r}
Gwynnda_Trash_Wheel_Collection_Data <- read_excel("202309 Trash Wheel Collection Data.xlsx", 
                sheet = "Gwynnda Trash Wheel",
                range = "A3:L160",
                col_names = c("Dumpster", 
                              "Month", "Year", "Date",                                         "Weight.tons",                                                   "Volume.cubic_yards", 
                              "Plastic.Bottles",
                              "Polystyrene", 
                              "Cigarette.Butts", 
                              "Plastic.Bags", "Wrappers", 
                              "Homes.Powered"))



Gwynnda_Trash_Wheel_Collection_Data.x <- Gwynnda_Trash_Wheel_Collection_Data %>% drop_na(Dumpster)%>% mutate(homes_powered = Weight.tons * 500/30,
                       origin = "Gwynnda_Trash_Wheel") 
                       
                       
Trash_Wheel_Collection_Data.x$Year <- as.numeric(Trash_Wheel_Collection_Data.x$Year)

data <- bind_rows(Trash_Wheel_Collection_Data.x,
                  Professor_Trash_Wheel_Collection_Data.x,
                  Gwynnda_Trash_Wheel_Collection_Data.x)


```



```{r}
sumw <-  data  %>%
  filter(origin == "Professor_Trash_Wheel") %>%
  pull(Weight.tons) %>%
  sum()

sumx <- data %>%
  filter(origin == "Gwynnda_Trash_Wheel" & Year == "2021" & Month == "July") %>%
  pull(Cigarette.Butts) %>%
  sum()


```

After merging the data, I have `r dim(data)[1]` observations and `r dim(data)[2]` variables. The total weight of trash collected by Professor Trash Wheel is `r sumw` and total number of cigarette butts collected by Gwynnda in July of 2021 is `r sumx`.




Problem 3


```{r}
MCI_baseline <- read.csv("MCI_baseline.csv", skip = 1)



```
I use read.csv to read the raw data, however the first contains the metadata, which describes the information of encoding. male = 1 female = 0. Thus I read the data from the second line command (skip =1).


```{r}

MCI_baseline.x <- MCI_baseline %>%
              mutate(Sex = ifelse(Sex == 1,"Male","Female"),
              apoe4 = ifelse(apoe4 == 1,"carriers", "Non-carriers")) 


Mean_age <- MCI_baseline.x %>% pull(Current.Age) %>% mean()



MCI_baseline.x %>% filter(Sex == "Female") %>% pull(apoe4) %>% table()


mci_amyloid <- read.csv("mci_amyloid.csv", skip = 1)

mci_amyloid.x <- mci_amyloid %>%
                  drop_na(Baseline) %>%  #remove non applicable value
                  filter(Baseline != "Na") #remove the artifical na value
```

There are `r dim(MCI_baseline.x)[1]` participants were recruited, and of these `r dim(nomissing.onset)[1]` develop MCI. The average baseline age is `r mean_age`. The proportion of women in the study are APOE4 carriers is `r 63/(63+148)`



```{r}

id_in_MCI_baseline <- MCI_baseline.x %>% filter(!ID %in% mci_amyloid.x$Study.ID)
id_in_mci_amyloid <- mci_amyloid.x %>% filter(!Study.ID %in% MCI_baseline.x$ID)



data <- MCI_baseline.x %>%
  rename(Study.ID = ID) %>%
  left_join(mci_amyloid.x, by ="Study.ID")

write.csv(data,"modified.data.csv")


```
Those ID are only in MCI_baseline but not in mci_amyloid: `r id_in_MCI_baseline$ID`, and Those ID are only in mci_amyloid but not in MCI_baseline: `r id_in_mci_amyloid$Study.ID`.


According to the exclusion criterion, I exclude the patients with missing baseline value. After combing the baseline and amyloid data, I have a dataset with `r dim(data)[1]` observations and `r dim(data)[2]` variables in a wide format. The data constains demograhpic charactors like sex and age, as well as baseline data and 4 visits for β 42/40 ratios.
